\section{Results and Discussion}

\subsection{Multi-component Simulations}
% Many numerical experiments were conducted to verify and validate this code.

% The interaction between components is demonstrated by an example simulation

\input{nuclide_base_cases}

\subsection{Single Effect Parametric Analyses}
% Many parametric analysis were conducted to validate system responses 
\input{sol_sensitivity}
\input{sol_results}

\FloatBarrier
\subsection{Significance}
% The existence of this code enables dynamic analysis of repository performance 
% during fuel cycle simulation.

This work has provided a flexible code for rapid mediuim fidelity calculation
of generic repository performance in the context of fuel cycle analysis.
Capable of hydrologic contaminant transport discussed here, thermal transport
demonstrated elsewhere, and integration within a fuel cycle simulation code,
\Cyder is the first of its kind.

In this work, key conceptual components and modeling methods for geologic
radioactive waste disposal were identified as part of a literature review,
dominant physics of thermal and radionuclide transport were identified by
conducting sensitivity analyses with detailed codes. Accordingly, a basic set
of abstracted models were developed and implemented within the \Cyder code.

A set of basic capabilities within the \Cyder library have been developed and
validated and an assortment of advanced features, data, testing, and plotting
capabilities are functional. The \Cyder source code in which these models are
implemented is made freely available to interested researchers and potential
model developers \cite{huff_cyder_2013}. In addition to the source code and
supporting publications, the \Cyder code is well commented and produces
clickable, browsable automated documentation with each build. That
documentation is also available online \cite{huff_cyder_2013}.

The application programming interface to this software library is intentionally
general, facilitating the incorporation of the models presented here within
external software tools in need of a multicomponent disposal system simulator.  

Furthermore, this work contributes to an expanding ecosystem of computational
models available for use with the Cyclus fuel cycle simulator. This hydrologic
nuclide transport library, by virtue of its capability to modularly integrate
with the Cyclus fuel cycle simulator has laid the foundation for integrated
disposal option analysis in the context of fuel cycle options.
