\section{Results and Discussion}
\label{sec:results}

In the present work, many numerical experiments successfully verified the \Cyder software library.
Multi-component simulations demonstrated expected transport behavior and
the successful collective interaction of the modular
components in a \Cyder repository. Single-parameter sensitivity analyses
demonstrated that physics captured by the \Cyder models compare favorably to
results reported in \cite{huff_key_2012} from a more detailed existing model,
the Clay \gls{GDSM}, developed by the \gls{UFD} Campaign within the
\gls{DOE} Office of Nuclear Energy \cite{clayton_generic_2011}.

In addition to these numerical experiments, a robust unit test suite was
deployed during development to verify \Cyder software implementation.
Finally, \Cyder was able to perform radionuclide transport calculations
rapidly, on timescales of a few minutes rather than the timescales of a few
hours seen in higher fidelity tools.

\subsection{Multi-component Simulations}
% Many numerical experiments were conducted to verify and validate this code.

% The interaction between components is demonstrated by an example simulation

\input{./results/nuclide_base_cases}

\subsection{Single Effect Parametric Analyses}
% Many parametric analysis were conducted to validate system responses
\input{./results/se}

\section{Conclusions}
% The existence of this code enables dynamic analysis of repository performance
% during fuel cycle simulation.

This paper has described the design, development, and verificiation of \Cyder, a
flexible software library for rapid medium-fidelity calculation of hydrologic
contaminant transport integrated within a fuel cycle simulation library.
In this work, four medium fidelity modeling methods for geologic radioactive waste disposal
performance analysis were described as was their implementation in the \Cyder
repository performance library.  This hydrologic
nuclide transport library, by virtue of its capability to modularly integrate
with the \Cyclus fuel cycle simulator has demonstrated a new capability for
integrated disposal options analysis when fuel cycle and and nuclear waste
disposal decisions are technologically coupled. 

\Cyder performance within the \Cyclus fuel cycle simulator and agreement
between Cyder and the more detailed stand-alone \gls{GDSM} model were also demonstrated.
While \Cyder methods make a strategic tradeoff between speed and fidelity, they were shown to capture
essential physics when computing back-end nuclear fuel cycle metrics. The
result is a library of medium-fidelity hydrologic contaminant transport models
within a disposal facility simulation framework appropriate for use in dynamic
nuclear fuel cycle simulators.

Finally, this work contributes to an expanding ecosystem of computational
models available for use with the \Cyclus fuel cycle simulator. 
Like those tools, the \Cyder source code is freely available to interested researchers and
potential model developers \cite{huff_cyder_2013}.  In addition to the source
code and supporting publications, the \Cyder library is well commented and
produces clickable, browsable automated documentation with each build. That
documentation is also available online. 

% Finally, the application programming
%interface to this software library is intentionally general, facilitating the
%incorporation of the models presented here within external software tools.

