The mass transfer interfaces between the mass balance models are essential to
the understanding of the \Cyder paradigm.  Depending on the mass balance model
selected in the external of two components, mass transfer into that component is
either explicit or implicit.

In the explicit mode, the mass transfer mode is chosen by the user. Available
options include  advective, dispersive,
coupled, or fixed flux. The corresponding transfer rate is calculated based on the conditions at the transfer
boundary. The inventory in the components is then updated based on this transfer
rate. While all components enable this on their outer boundary, only the mass
balance models that are 0-dimensional in space (the Degradation Rate model and
the Mixed Cell model) require explicit transfer on their inner boundary.

In the implicit mode, the mass balance model of the external component determines
the inventory based on boundary conditions provided by the internal component.
The appropriate mass is then transferred to accomplish the change in inventory.

In groundwater transport, contaminants are transported by dispersion and
advection such that the mass conservation equationfor mass flux
becomes \cite{schwartz_fundamentals_2004, wang_introduction_1982,
van_genuchten_analytical_1982}:

     \begin{align}
      J &= J_{dis} + J_{adv}
      \intertext{where}
      J_{dis} &= \mbox{ Total Dispersive Mass Flux }[kg/m^2/s]\nonumber\\
      J_{adv} &= \mbox{ Advective Mass Flux }[kg/m^2/s].\nonumber
      \end{align}

It is customary to define the combination of molecular diffusion and
mechanical mixing as the dispersion tensor, $D$, such that, for a conservative
solute (infinitely soluble and non-sorbing), so that the dispersive component
can be described in terms of the concentration profile:

    \begin{align}
      J_{dis} &= \mbox{ Total Dispersive Mass Flux }[kg/m^2/s]\nonumber\\
      &= -\theta(D_{mdis} + \tau D_m)\nabla C \nonumber\\
      &= -\theta D\nabla C \nonumber
      \intertext{where}
      \theta &= \mbox{ Porosity }[-] \nonumber\\
      \tau &= \mbox{ Tortuosity }[-] \nonumber\\
      C &= \mbox{ Concentration }[kg/m^3]\nonumber\\
      D_m &= \mbox{ Molecular diffusion coefficient }[m^2/s]\nonumber\\
      D_{mdis} &= \mbox{ Coefficient of mechanical dispersivity}[m^2/s]\nonumber\\
      D &= \mbox{ Effective Dispersion Coefficient }[m^2/s].\nonumber
    \end{align}

Meanwhile, the advective mass flux depends on the concentration, the porosity
of the medium, and the fluid velocity in that medium,

    \begin{align}
      J_{adv} &= \mbox{ Advective Mass Flux }[kg/m^2/s]\nonumber\\
      &= \theta vC\nonumber\\
      v &= \mbox{ Fluid Velocity in the medium }[m/s].\nonumber
    \end{align}

For uniform flow in $\hat{k}$,
    \begin{align}
      J &=\left(-\theta D_{xx} \frac{\partial C}{\partial x}
             \right)\hat{\imath}
             + \left( -\theta D_{yy} \frac{\partial C}{\partial y}
            \right)\hat{\jmath}\nonumber\\
            &+ \left( -\theta D_{zz} \frac{\partial C}{\partial z}
             + \theta v_zC \right)\hat{k}.
      \label{unidirflow}
    \end{align}

Solutions to this equation can be categorized by their boundary conditions.
Those boundary conditions serve as the interfaces between components in the
\Cyder library of nuclide transport models by way of advective, dispersive,
coupled, and fixed fluxes.  This is supported by implementation in which
vertical advective velocity, $v_z$, is uniform throughout the system and in which
characteristic geologic and material parameters such as the dispersion
coefficient are known for each component.

The mass transfer modes available in \Cyder represent a range of boundary
conditions. The following sections cover the mathematical models defining those
that have been implemented and how they relate to the mass balance models in
Section \ref{sec:mass_balance}.
